

## Figures

### Figures from local files or the internet

Figures and tables are important tools to present results or illustrate important aspects of your thesis.
Just as LaTeX, Word, OpenOffice or Pages, RMarkdown allows you to include figures from files such as .png or .pdf or websites.
The syntax is quite simple, just use

    ![Caption](Source){width=100%}

The source can be a file on your computer like in the example below, or a web address.

![Example figure, Source: [Allison Horst](https://github.com/allisonhorst/stats-illustrations).](FIGURES/rmarkdown_rockstar.png){width="75%"}

## Figures from R plots

Thanks to the unique combination of R Code and text, you can also directly present R plots and add a caption.
Just see this example:

```{r example_figure, fig.cap = "A dangerous animal. Source: [Allison Horst]( https://github.com/allisonhorst/stats-illustrations).", fig.height = 4, fig.width = 6}

data <- read.csv(sharkdata)
plot(data$x, data$y, xlab = "", ylab = "")

```

Rather than using `{width=75%}` to control the size of the figure, just use the chunk options above.
In most cases this is trial and error to get the looks right[^2], so feel free to change the settings above.
Note that the figure won't necessarily show up right below the chunk in order to manage the space efficiently.

[^2]: For example, the shark looks far less dangerous (chubby, even), if you use `fig.height = 5` above.

## Tables

### kable

Tables are another important tool to present information.
RMarkdown provides several ways to include tables.
A simple way to print data frames -- for example a table with summary statistics -- is the `knitr` function `kable` (presumably stands for "knit table").

```{r example_table}
example_data <- read.csv("DATA/example_data.csv")
kable(example_data,
      booktabs = TRUE,
      digits = 2,
      caption = "Example Table with kable.") 
```

The option `booktabs = TRUE` uses the LaTeX booktabs package which produces nice tables without vertical lines.
The option `digits= 2` should be self-explanatory.
To see more options, visit the documentation for `kable` or use the help function in your R console.

### Markdown tables

Markdown comes with a native syntax to set tables which is different from LaTeX or html, but very simple.
Just to give you an example:

    | A           |  Simple       | Table |
    |-------------|:-------------:|------:|
    | First col.  |  left-aligned | More  |
    | Second col. |    centered   | data  |
    | Third col.  | right-aligned | here  |

    Table: Your Caption

The `:` indicate the alignment of the table.
This is how it looks like once you write it outside a code chunk:

| A           |    Simple     | Table |
|-------------|:-------------:|------:|
| First col.  | left-aligned  |  More |
| Second col. |   centered    |  data |
| Third col.  | right-aligned |  here |

: Example Table in Markdown.

### LaTeX tables

If you are used to LaTeX already, it might be natural to continue using LaTeX syntax for tables.
RMarkdown supports this.

    \begin{table}[]
      \caption{Example Table in LaTex.}
      \begin{tabular}{lcr}
      \toprule
      A           & LaTeX         & Table \\ \midrule
      First col.  & left-aligned  & More  \\
      Second col. & centered      & data  \\
      Third col.  & right-aligned & here 
      \end{tabular}
    \end{table}

Once you write this outside a chunk, this is how it will turn out:

```{=tex}
\begin{table}[!htp]
  \caption{Example Table in LaTex.}
  \begin{center}
  \begin{tabular}{lcr}
  \toprule
  A           & LaTeX         & Table \\ \midrule
  First col.  & left-aligned  & More  \\
  Second col. & centered      & data  \\
  Third col.  & right-aligned & here  \\ \bottomrule
  \end{tabular}
  \end{center}
\end{table}
```
LaTeX tables come with a nice option called floats.
By adding `!htp` between the brackets in `\begin{table}[!htp]`, you can tell LaTeX to put the table (h)ere, at the (t)op of the page or on its own (p)age.
Those options will be prioritized in this order.

### Tables generator

Setting the tables manually is quite difficult.
The website [tablesgenerator.com](https://www.tablesgenerator.com) is a nice interface to paste information into tables and make adjustments such as alignments etc.
You can choose between LaTeX and Markdown tables, the functionalities of LaTeX are a little more advanced.