---
# Required Information --------------------------------------------------------
# change lines 4 - 18
title: "Thesis Title"
author1: "Max Mustermann"
adress_street_and_no1: "Königsworther Platz 1"
postcode1: "30167"
place1: "Hannover"
matriculation_number1: "1234567"
semester1: "1"
course_of_study1: "Wirtschaftswissenschaft"

# if you write in a team, put the data of the second author here:
author2: "Melissa Musterfrau"
adress_street_and_no2: "Königsworther Platz 2"
postcode2: "30167"
place2: "Hannover"
matriculation_number2: "7654321"
semester2: "2"
course_of_study2: "Wirtschaftswissenschaft"

# if you write in a team, put the data of the third author here:
author3: "Maxi Musterperson"
adress_street_and_no3: "Königsworther Platz 3"
postcode3: "30167"
place3: "Hannover"
matriculation_number3: "1235813"
semester3: "3"
course_of_study3: "Wirtschaftswissenschaft"

date: "31.03.2020"

university: "Leibniz Universität Hannover"
faculty: "Wirtschaftswissenschaftliche Fakultät" 
institute: "Institut für Banken und Finanzierung"
advisor: "Prof. Dr. Maik Dierkes"
altadvisor: "M.Sc. Sebastian Schrön"            
module: "Hedge Funds: Trading Strategies and Performance Evaluation"
module_number: "374040"
#Change to "de" for German Inhaltsverzeichnis, Tabellenverzeichnis etc.
lang: "en-us"
#
output: 
  pdf_document:
    template: ibf_template.tex  
    number_sections: true
    toc: true
    toc_depth: 3
    highlight: tango
    keep_tex: false
geometry: "a4paper, left=3cm,right=5cm,top=3cm,bottom=3cm"
bibliography: bibliography.bib
csl: CSL/apa.csl
fontsize: 12pt
linestretch: 1.5
lof: true
lot: true
---



```{r setup, include=FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)

sharkdata <- "https://raw.githubusercontent.com/allisonhorst/stats-illustrations/master/other-stats-artwork/shark_raw.csv"

library(tidyverse)
library(lubridate)
library(nycflights13)
library(knitr)
library(kableExtra)

```

# Introduction



# Figures

## Figures from ggplot


```{r example_figure, fig.cap = "A dangerous animal. Source: [Allison Horst.](https://github.com/allisonhorst/stats-illustrations)", fig.height = 3, fig.width = 6}

data <- read_csv(sharkdata)
ggplot(data=data, aes(x=x, y = y)) + geom_point(size=0.1)
```


## Figures from local files

This is the easiest way to include a figure from a local file:

![Faces of debugging. Source: [Allison Horst](https://github.com/allisonhorst/stats-illustrations)  ](FIGURES/debugging.jpg)


# Tables

## Markdown tables


## Kable



This is an example table with kable, including a caption:

```{r example_table}

kable(flights[1:5,1:5],
      booktabs = TRUE,
      caption = "Example Table.") 

```

## LaTeX tables

# Citations

## Citations in Markdown

Dummy citation to force RMarkdown to produce references: @wickham_r_2016

## Citations in LaTeX

## Citation styles

# Conclusion





# Literature