---
title: "Thesis Title"
author1: "Max Mustermann"
adress_street_and_no1: "Königsworther Platz 1"
postcode1: "30167"
place1: "Hannover"
matriculation_number1: "1234567"
semester1: "1"
course_of_study1: "Wirtschaftswissenschaft"
# if you write in a team, put the data of the second author here:
author2: "Melissa Musterfrau"
adress_street_and_no2: "Königsworther Platz 2"
postcode2: "30167"
place2: "Hannover"
matriculation_number2: "7654321"
semester2: "2"
course_of_study2: "Wirtschaftswissenschaft"
# if you write in a team, put the data of the third author here. If you write in a team of two, just remove the next 7 lines:
author3: "Maxi Musterperson"
adress_street_and_no3: "Königsworther Platz 3"
postcode3: "30167"
place3: "Hannover"
matriculation_number3: "1235813"
semester3: "3"
course_of_study3: "Wirtschaftswissenschaft"
date: "31.03.2022"
university: "Leibniz University Hannover"
faculty: "School of Economics and Management" 
institute: "Institute of Banking and Finance"
advisor: "Prof. Dr. Maik Dierkes"
altadvisor: "M.Sc. Sebastian Schrön"            
module: "Hedge Funds: Trading Strategies and Performance Evaluation"
# Belegnummer:
module_number: "374040"
lang: "en-us"
output: 
  pdf_document:
    template: ibf_template.tex
    extra_dependencies:
    - dcolumn
    toc: true
    toc_depth: 3
    highlight: tango
    keep_tex: false
    number_sections: true
geometry: "a4paper, left=2cm,right=5cm,top=3cm,bottom=3cm"
bibliography: BIB/example_bibliography.bib
csl: CSL/apa.csl
fontsize: 11pt
linestretch: 1.5
lof: true
lot: true
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)



sharkdata <- "https://raw.githubusercontent.com/allisonhorst/stats-illustrations/master/other-stats-artwork/shark_raw.csv"


library(knitr)
library(tidyverse)

```

# Introduction

```{r child='01_Introduction.Rmd'}
```

# Language

```{r child='02_Language.Rmd'}
```

# Equations

```{r child='03_Equations.Rmd'}
```

# Figures and Tables

```{r child='04_Figures_and_Tables.Rmd'}
```


# Citations

```{r child='05_Citations.Rmd'}
```

# Debugging

```{r child='06_Debugging.Rmd'}
```


# Additional Features 

```{r child='07_Additional_Features.Rmd'}
```


# How to get started

Now to get started and put this template to use, just save it in your working directory, get rid of all the stuff above and start with your thesis.
This document is work in progress, so if you encounter any unsolvable issues, write an e-mail to [Sebastian Schrön](mailto:sebastian.schroen@finance.uni-hannover.de)


<!-- this command \appendix changes the numbering of sections to alphabetical -->

\appendix

# Contributions

```{r child='A1_Contributions.Rmd'}
```



<!-- Makes sure to have a new page for your literature -->

\newpage

# Literature
