---
title: "Thesis Title"
author1: "Max Mustermann"
adress_street_and_no1: "Königsworther Platz 1"
postcode1: "30167"
place1: "Hannover"
matriculation_number1: "1234567"
semester1: "1"
course_of_study1: "Wirtschaftswissenschaft"
# if you write in a team, put the data of the second author here:
author2: "Melissa Musterfrau"
adress_street_and_no2: "Königsworther Platz 2"
postcode2: "30167"
place2: "Hannover"
matriculation_number2: "7654321"
semester2: "2"
course_of_study2: "Wirtschaftswissenschaft"
# if you write in a team, put the data of the third author here. If you write in a team of two, just remove the next 7 lines:
author3: "Maxi Musterperson"
adress_street_and_no3: "Königsworther Platz 3"
postcode3: "30167"
place3: "Hannover"
matriculation_number3: "1235813"
semester3: "3"
course_of_study3: "Wirtschaftswissenschaft"
date: "31.03.2022"
university: "Leibniz University Hannover"
faculty: "School of Economics and Management" 
institute: "Institute of Banking and Finance"
advisor: "Prof. Dr. Maik Dierkes"
altadvisor: "M.Sc. Sebastian Schrön"            
module: "Hedge Funds: Trading Strategies and Performance Evaluation"
# Belegnummer:
module_number: "374040"
lang: "en-us"
output: 
  pdf_document:
    template: ibf_template.tex
    extra_dependencies:
    - dcolumn
    toc: true
    toc_depth: 3
    highlight: tango
    keep_tex: false
    number_sections: true
geometry: "a4paper, left=2cm,right=5cm,top=3cm,bottom=3cm"
bibliography: BIB/example_bibliography.bib
csl: CSL/apa.csl
fontsize: 11pt
linestretch: 1.5
lof: true
lot: true
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)



sharkdata <- "https://raw.githubusercontent.com/allisonhorst/stats-illustrations/master/other-stats-artwork/shark_raw.csv"


library(knitr)
library(tidyverse)

```

# Introduction

```{r child='01_Introduction.Rmd'}
```

# Language

```{r child='02_Language.Rmd'}
```

# Equations

```{r child='03_Equations.Rmd'}
```

# Figures and Tables

```{r child='04_Figures_and_Tables.Rmd'}
```


# Citations

```{r child='05_Citations.Rmd'}
```

# Debugging

```{r child='06_Debugging.Rmd'}
```

# Additional LaTeX features

Some experienced LaTeX users might feel that the basic functions of this template are insufficient.
To add packages, just add them to the extra dependencies in the header in the following way:

    extra_dependencies:
        - dcolumn
        - newpackage1
        - newpackage2

# How to get started

Now to get started and put this template to use, just save it in your working directory, get rid of all the stuff above and start with your thesis.
This document is work in progress, so if you encounter any unsolvable issues, write an e-mail to [Sebastian Schrön](mailto:sebastian.schroen@finance.uni-hannover.de)


\appendix

# Contributions

If your thesis needs an appendix, simply use `\appendix` to separate the main body of your thesis from the appendix.
The sections will have alphabetic enumeration instead of Arabic numbers to indicate appendices.
Ideally, use `\newpage` to start the appendix on a new page.

If you write as a group, one appendix should be dedicated to the contribution of each student.
Please edit the following table accordingly to highlight which student contributed to which section:

| Section | Student            |
|--------:|--------------------|
|       1 | Melissa Musterfrau |
|     2.1 | Maxi Musterperson  |
|     2.2 | Maxi Musterperson  |
|     3.1 | Max Mustermann     |
|     ... | ...                |

Hint: Use the tablesgenerator.com for this table.

Finally, please state whether you want a joint of individual evaluation of your thesis by altering the following sentence:

We decided for a joint evaluation of the thesis.

\newpage

# Literature
